Manuscript draft

### 2024-04-09 docs/manuscript.qmd
calculated report stats for cleaning steps and began incorporating them into the manuscript

```{r}
#| include: false
library(tidyverse)
library(here)
```

@@

```{r}
#| include: false
load(here("data/dataPrep/dataPrep_report_stats.Rda"))
dp <- dataPrep_report_stats
cl <- which(dp$dataset == "data_cleaned")
pctremovedcleaned <- round(100*(dp$nrow[[cl-1]] - dp$nrow[[cl]])/(dp$nrow[[cl-1]]), 2)
```

@@

```{r}
#| include: false
soc <- which(dp$dataset == "downsampled_10min_forSocial")
vulturessoc <- unique(unlist(dp$vultures[[soc]]))
nvulturessoc <- length(vulturessoc)
nvulturessoc_szns <- dp$nvultures[[soc]]
```

After this cleaning, the data used for social network analysis contained `r nvulturessoc` unique vultures in total (range: `r min(nvulturessoc_szns)`-`r max(nvulturessoc_szns)`; mean = `r round(mean(nvulturessoc_szns), 2)` vultures per season, sd = `r round(sd(nvulturessoc_szns), 2)` vultures per season).

@@

```{r}
#| include: false
mov <- which(dp$dataset == "downsampled_10min")
vulturesmov <- unique(unlist(dp$vultures[[mov]]))
nvulturesmov <- length(vulturesmov)
nvulturesmov_szns <- dp$nvultures[[mov]]
```

>>>>

```{r}
#| include: false
library(tidyverse)
library(here)
tar_config_set(store = here::here('_targets'))
```

@@

```{r}
tar_load(cleaned_r)
tar_load(joined0_r)
pctremovedcleaned <- (joined0_r[1]-cleaned_r[1])/joined0_r[1]
```

@@

```{r}
tar_load(downsampled_10min_forSocial_r)
nvultures <- map_dbl(downsampled_10min_forSocial_r, "vultures")
```

After this cleaning, the data used for social network analysis contained between `r min(nvultures)` and `r max(nvultures)` vultures per season (mean = `r mean(nvultures)`; sd = `r sd(nvultures)`).

@@

```{r}
tar_load(downsampled_10min_r)
nvultures <- map_dbl(downsampled_10min_r, "vultures")
```
